Topic Modeling of News

### 2017-10-25 paper/R/03_explore.Rmd
add lda model

## Load Data
```{r}
rm(list = ls())
load("../output/news_cleaned.Rda")

@@

# Pre-Process Text

```{r, echo=FALSE, message=FALSE, warning=FALSE}
clean.text = function(x)
  {
  x = gsub("DIE WELT", "", x)
  x = gsub("SPIEGEL ONLINE", "", x)
  x = gsub("FOCUS Online", "", x)
  x = gsub("ZEIT ONLINE", "", x)
  x = gsub("stern de", "", x)
  x = gsub("Handelsblatt", "", x)
  x = gsub("Politik Inland Bild de", "", x)
  x = gsub("BILDplus Inhalt", "", x)
  x = gsub("Bild de", "", x)
  x = gsub("SWR Aktuell", "", x)
  x = gsub("SWR de", "", x)
  x = gsub("[ ]NDR[ ]", "", x)
  x = gsub('ZDF \"\"Morgenmagazin\"\"', "", x)
  x = gsub("ZDFmediathek", "", x)
  x = gsub("[ ]ZDF[ ]", "", x)
  x = gsub("[ ]ARD[ ]", "", x)

  x = gsub("die neuesten Nachrichten", "", x)
  x = gsub("RSS Feed", "", x)
  x = gsub("Der Überblick   7 mal 17   Alle Artikel", "", x)
  x = gsub("Der Tag im Überblick", "", x)
  x = gsub("Inhalt Seite 1", "", x)
  x = gsub("Seite 2", "", x)
  x = gsub("dpa", "", x)
  x = gsub("Twitter Anzeige", "", x)
  x = gsub("Anzeige", "", x)
  x = gsub("Foto  \\w+", "", x)
  x = gsub("Video", "", x)
  x = gsub("Quelle \\w+", "", x)
  x = gsub("\\w+ \\w+ Getty Images", "", x)
  x = gsub("AFP", "", x)
  x = gsub("August", "", x)
  x = gsub("Live-Ticker", "", x)
  x = gsub("Deutsche Presse Agentur GmbH   Nachrichtenagentur Alle Beiträge von  anzeigen", "", x)
  x = gsub("Deutsche Presse Agentur", "", x)

  x = gsub("[[:punct:]]", " ", x)  # replace punctuation with space
  x = gsub("[[:cntrl:]]", " ", x)  # replace control characters with space
  x = gsub("[[:digit:]]", "", x)  # remove numbers
  x = gsub("^[[:space:]]+", "", x) # remove whitespace at beginning of documents
  x = gsub("[[:space:]]+$", "", x) # remove whitespace at end of documents 
  x = gsub("[\n{2,}]", "", x)
  x = tolower(x)
  return(x)
}

# apply function to the "orig" dataframe
btw$text_cleaned <- clean.text(btw$text)
```

## Remove Stopwords
```{r}
df$text_cleaned<- removeWords(df$text, stopwords("german"))
```

@@

### Add customized stopwords
```{r}
mystopwords <- c("ich","sie","passwort","uhr","bitte","videolänge","dass","mindestens","das","mail","die","zdf","schon","die","neuer abschnitt", "datenschutzerklärung","premium","nutzungsbedingungen","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","swr","fullscreen","wochit","statista","club","sagte","mehr")

btw$text_cleaned<- removeWords(btw$text_cleaned, mystopwords)
```

>>>>

## Load Data
```{r}
rm(list = ls())
load("../output/news_cleaned2.Rda")

@@

@@

### 2017-10-25 paper/R/04_reduced.Rmd
add lda model

```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer",
          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
lapply(libs, library, character.only = TRUE)
```

## Load Data
```{r}
rm(list = ls())
load("../output/news_cleaned2.Rda")

col <- brewer.pal(12, name = "Paired")
```

## Summary Stats
```{r}
df %>%
  group_by(site) %>%
  summarise(obs = n(),
    fb_shares.mean = mean(fb_shares),
            fb_shares.max = max(fb_shares),
            fb_likes.mean = mean(fb_likes),
            fb_likes.max = max(fb_likes),
            external_links.mean = mean(external_links),
            external_links.max = max(external_links),
            text_length.mean = mean(text_lenght),
            text_length.max = max(text_lenght)) %>%
  htmlTable(align = "l")
```

### Text Length
```{r}
ggplot(df, aes(x=as.factor(site), y=text_lenght)) +
  stat_summary(fun.y="median", geom="bar", fill = "blue", alpha = .5) +
  labs(title = "") +
  labs(x="", y="Median Text Length") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

### Facebook Likes
```{r}
ggplot(df, aes(x=as.factor(site), y=fb_likes)) +
  stat_summary(fun.y="sum", geom="bar", fill = "blue", alpha = .5) +
  labs(title = "") +
  labs(x="", y="Sum of Facebook Likes") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

## Tokenize terms
```{r}
news_words <- df %>%
  unnest_tokens(word, text) %>%
  count(site, word, sort = TRUE)

## TF-IDF
news_words <- news_words %>%
  bind_tf_idf(word, site, n)

### Terms with high tf-idf
news_words %>%
  #filter(site == "spiegel.de") %>%
  arrange(desc(n))
```

## Tokenize terms
```{r}
news_words <- btw %>%
  unnest_tokens(word, text_cleaned) %>%
  count(site, word, sort = TRUE)

## TF-IDF
news_words <- news_words %>%
  bind_tf_idf(word, site, n)

### Terms with high tf-idf
news_words %>%
  #filter(site == "spiegel.de") %>%
  arrange(desc(n))
```

## Bigrams

```{r}
news_bigrams <- btw %>%
  unnest_tokens(bigram, text_cleaned, token="ngrams", n=2)

news_bigrams %>%
  count(bigram, sort = TRUE)
```

# Topic Modeling
## LDA
```{r}
# Build corpus
btw.lda <- Corpus(VectorSource(btw$text_cleaned))
# Create document-term matrix
dtm <- DocumentTermMatrix(btw.lda)

@@

```{r}
# Run LDA using Gibbs sampling
library(topicmodels)

#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
burnin <- 4000
iter <- 2000
thin <- 500
seed <-list(2003,5,63,100001,765)
nstart <- 5
best <- TRUE

k = 10 # Topics
```

```{r}
t1 <- Sys.time()
lda10 <-LDA(dtm, k, method="Gibbs", control=list(nstart=nstart, seed=seed, best=best, burnin=burnin, iter = iter, thin=thin))
t2 <- Sys.time()
t2 - t1
```

```{r}
#write out results
lda10.topics <- as.matrix(topics(lda10))
lda10.topics
```

```{r}
#top 6 terms in each topic
lda10.terms <- as.matrix(terms(lda10,6))
```

```{r}
#probabilities associated with each topic assignment
topicProbabilities <- as.data.frame(lda10@gamma)
```

@@

>>>>

```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer","topicmodels",
          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
lapply(libs, library, character.only = TRUE)
```

## Load Data
```{r}
rm(list = ls())

load("../output/news_cleaned2.Rda")
write.csv(btw, file="../output/btw.csv")

df$date <- as.Date(df$date)

#col <- brewer.pal(12, name = "Paired")
```

## Reduce Dataframe
```{r}
df %>%
  filter(fb_shares > 0) %>%
  filter(!site %in% c("ndr.de","wdr.de")) %>%
  filter(grepl("bundestagswahl", text_cleaned)) -> btw

## Summary Stats
```{r}
btw %>%
  group_by(site) %>%
  summarise(obs = n(),
    fb_shares.mean = mean(fb_shares),
            fb_shares.max = max(fb_shares),
            fb_likes.mean = mean(fb_likes),
            fb_likes.max = max(fb_likes),
            external_links.mean = mean(external_links),
            external_links.max = max(external_links),
            text_length.mean = mean(text_lenght),
            text_length.max = max(text_lenght)) %>%
  htmlTable(align = "l")
```

### Text Length
```{r}
ggplot(btw, aes(x=as.factor(site), y=text_lenght)) +
  stat_summary(fun.y="median", geom="bar", fill = "blue", alpha = .5) +
  labs(title = "") +
  labs(x="", y="Median Text Length") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

### Facebook Likes
```{r}
ggplot(btw, aes(x=as.factor(site), y=fb_likes)) +
  stat_summary(fun.y="median", geom="bar", fill = "blue", alpha = .5) +
  labs(title = "") +
  labs(x="", y="Median of Facebook Likes") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

## What are the news with the highest fb-shares?
```{r}
btw %>%
  filter(site == "tagesschau.de") %>%
  arrange(desc(fb_shares)) %>%
  select(text) %>%
  .[1,]
```

```{r}
btw %>%
  ggplot(aes(date, fill = site)) +
  geom_histogram(bins = 100, alpha = .8)
```

## Tokenize
```{r}
btw %>%
  unnest_tokens(word, text_cleaned) %>%
  count(site, word, sort = TRUE) -> news_count

## TF-IDF
news_count <- news_count %>%
  bind_tf_idf(word, site, n)

### Terms with high tf-idf
news_count %>%
  #filter(site == "spiegel.de") %>%
  arrange(desc(tf_idf))
```

### Bigrams
```{r}
btw %>%
  unnest_tokens(bigram, text_cleaned, token="ngrams", n=2) %>%
  count(site, bigram, sort = TRUE) -> news_bigrams

news_bigrams
```

# Topic Modeling
## Build Corpus
```{r}
btw %>%
  filter(nchar(text_cleaned) > 5) -> btw
```

```{r}
# Build corpus
df.lda <- Corpus(VectorSource(btw$text_cleaned))
# Create document-term matrix
dtm <- DocumentTermMatrix(df.lda)

@@

## Select Number of K Topics
(http://davidmeza1.github.io/2015/07/20/topic-modeling-in-R.html)

```{r}
seqk <- seq(30, 100, 5) #
burnin <- 1000
iter <- 1000
keep <- 50
system.time(fitted_many <- lapply(seqk, function(k) topicmodels::LDA(dtm, k = k,
                                                     method = "Gibbs",control = list(burnin = burnin,
                                                                         iter = iter, keep = keep) )))
```

### The harmonic mean function
```{r}
harmonicMean <- function(logLikelihoods, precision = 2000L) {
  llMed <- median(logLikelihoods)
  as.double(llMed - log(mean(exp(-mpfr(logLikelihoods,
                                       prec = precision) + llMed))))
}
```

# Run LDA using Gibbs sampling
```{r}
#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
burnin <- 1000
iter <- 1000
keep <- 50

k = 50 # Topics
```

```{r}
t1 <- Sys.time()
lda50 <-LDA(dtm, k, method="Gibbs", control=list(burnin=burnin, iter = iter, keep = keep))
t2 <- Sys.time()
t2 - t1

save(ldaOut, file=paste("../output/models/LDAGibbs",k,".Rda"))
```

```{r}
#write out results (docs to topics)
ldaOut.topics <- as.matrix(topics(ldaOut))
write.csv(ldaOut.topics,file=paste("../output/models/LDAGibbs",k,"DocsToTopics.csv"))
```

```{r}
#top 6 terms in each topic
ldaOut.terms <- as.matrix(terms(ldaOut,6))
write.csv(ldaOut.terms,file=paste("../output/models/LDAGibbs",k,"TopicsToTerms.csv"))
```

```{r}
#probabilities associated with each topic assignment
topicProbabilities <- as.data.frame(ldaOut@gamma)
rownames(topicProbabilities) <- make.unique(btw$title)

write.csv(topicProbabilities,file=paste("../output/models/LDAGibbs",k,"TopicProbabilities.csv"))
```

@@

```{r}
#write to file
write.csv(topic1ToTopic2,file=paste("../output/models/LDAGibbs",k,"Topic1ToTopic2.csv"))
write.csv(topic2ToTopic3,file=paste("../output/models/LDAGibbs",k,"Topic2ToTopic3.csv"))
```

### 2017-10-25 paper/R/06_stm.Rmd
add lda model

## Summary Stats
```{r}
btw %>%
  group_by(site) %>%
  summarise(obs = n(),
    fb_shares.mean = mean(fb_shares),
            fb_shares.max = max(fb_shares),
            fb_likes.mean = mean(fb_likes),
            fb_likes.max = max(fb_likes),
            external_links.mean = mean(external_links),
            external_links.max = max(external_links),
            text_length.mean = mean(text_lenght),
            text_length.max = max(text_lenght)) %>%
  htmlTable(align = "l")
```

### Text Length
```{r}
ggplot(btw, aes(x=as.factor(site), y=text_lenght)) +
  stat_summary(fun.y="median", geom="bar", fill = "blue", alpha = .5) +
  labs(title = "") +
  labs(x="", y="Median Text Length") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

### Facebook Likes
```{r}
ggplot(btw, aes(x=as.factor(site), y=fb_likes)) +
  stat_summary(fun.y="median", geom="bar", fill = "blue", alpha = .5) +
  labs(title = "") +
  labs(x="", y="Median of Facebook Likes") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

## What are the news with the highest fb-shares?
```{r}
btw %>%
  filter(site == "tagesschau.de") %>%
  arrange(desc(fb_shares)) %>%
  select(text) %>%
  .[1,]
```

```{r}
btw %>%
  ggplot(aes(date, fill = site)) +
  geom_histogram(bins = 100, alpha = .8)
```

## Tokenize
```{r}
btw %>%
  unnest_tokens(word, text_cleaned) %>%
  count(site, word, sort = TRUE) -> news_count

## TF-IDF
news_count <- news_count %>%
  bind_tf_idf(word, site, n)

### Terms with high tf-idf
news_count %>%
  #filter(site == "spiegel.de") %>%
  arrange(desc(tf_idf))
```

### Bigrams
```{r}
btw %>%
  unnest_tokens(bigram, text_cleaned, token="ngrams", n=2) %>%
  count(site, bigram, sort = TRUE) -> news_bigrams

news_bigrams
```

# Topic Modeling
## Build Corpus
```{r}
btw %>%
  filter(nchar(text_cleaned) > 5) -> btw
```

```{r}
# Build corpus
df.lda <- Corpus(VectorSource(btw$text_cleaned))
# Create document-term matrix
dtm <- DocumentTermMatrix(df.lda)

inspect(dtm)
```

## Select Number of K Topics
(http://davidmeza1.github.io/2015/07/20/topic-modeling-in-R.html)

```{r}
seqk <- seq(30, 100, 5) #
burnin <- 1000
iter <- 1000
keep <- 50
system.time(fitted_many <- lapply(seqk, function(k) topicmodels::LDA(dtm, k = k,
                                                     method = "Gibbs",control = list(burnin = burnin,
                                                                         iter = iter, keep = keep) )))
```

### The harmonic mean function
```{r}
harmonicMean <- function(logLikelihoods, precision = 2000L) {
  llMed <- median(logLikelihoods)
  as.double(llMed - log(mean(exp(-mpfr(logLikelihoods,
                                       prec = precision) + llMed))))
}
```

# Run LDA using Gibbs sampling
```{r}
#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
burnin <- 1000
iter <- 1000
keep <- 50

k = 50 # Topics
```

```{r}
t1 <- Sys.time()
lda50 <-LDA(dtm, k, method="Gibbs", control=list(burnin=burnin, iter = iter, keep = keep))
t2 <- Sys.time()
t2 - t1

save(ldaOut, file=paste("../output/models/LDAGibbs",k,".Rda"))
```

```{r}
#write out results (docs to topics)
ldaOut.topics <- as.matrix(topics(ldaOut))
write.csv(ldaOut.topics,file=paste("../output/models/LDAGibbs",k,"DocsToTopics.csv"))
```

```{r}
#top 6 terms in each topic
ldaOut.terms <- as.matrix(terms(ldaOut,6))
write.csv(ldaOut.terms,file=paste("../output/models/LDAGibbs",k,"TopicsToTerms.csv"))
```

```{r}
#probabilities associated with each topic assignment
topicProbabilities <- as.data.frame(ldaOut@gamma)
rownames(topicProbabilities) <- make.unique(btw$title)

write.csv(topicProbabilities,file=paste("../output/models/LDAGibbs",k,"TopicProbabilities.csv"))
```

```{r}
#Find relative importance of top 2 topics
topic1ToTopic2 <- lapply(1:nrow(dtm),function(x)
sort(topicProbabilities[x,])[k]/sort(topicProbabilities[x,])[k-1])
```

```{r}
#Find relative importance of second and third most important topics
topic2ToTopic3 <- lapply(1:nrow(dtm),function(x)
sort(topicProbabilities[x,])[k-1]/sort(topicProbabilities[x,])[k-2])
```

```{r}
#write to file
write.csv(topic1ToTopic2,file=paste("../output/models/LDAGibbs",k,"Topic1ToTopic2.csv"))
write.csv(topic2ToTopic3,file=paste("../output/models/LDAGibbs",k,"Topic2ToTopic3.csv"))
```

>>>>

# Topic Modeling
